Integration of Multiple Constraints in ACG

### 2013-09-22 lenls/paper.tex
LENLS: Live feedback from Maxime

\mainmatter              % start of the contributions
%
\title{Integration of Multiple Constraints in ACG}
%
\titlerunning{Constraints in ACG}  % abbreviated title (for running head)
%                                    also used for the TOC unless
%                                    \toctitle is used
%
\author{Jiří Maršík\inst{1,2,3} \and Maxime Amblard\inst{1,2,3}}
%
\authorrunning{Maršík et al.} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\tocauthor{Jiří Maršík and Maxime Amblard}
%
\institute{Université de Lorraine, Laboratoire lorrain de recherche en informatique et ses applications, UMR 7503, Vandoeuvre-lès-Nancy, 54500, France\\
\email{\{jiri.marsik, maxime.amblard\}@loria.fr},\\
\and
INRIA, Villers-lès-Nancy, 54600, France\\
\and
CNRS, Loria, Vandoeuvre-lès-Nancy, UMR 7503, 54500, France}

@@

\section{Motivation}

@@

@@

@@

If we were to use this approach to write a grammar that enforces multiple
constraints at the same time, we would end up with complicated types, like the
one below, which provide complete specifications of the various possible
situations (in this hypothetical grammar ($C$), the preposition \emph{de} has
12 different types).

@@

We would like to have a system which would be characterized by a diagram like
the one on Figure~\ref{fig:gacg} where the constraint signatures delimit the
legal syntactic structures independently of each other and without interfering
with the syntax-semantics interface. However, ACG diagrams are limited to
arborescences and we are obliged to generalize them in order to get
the expected interpretation of Figure~\ref{fig:gacg}.

@@

While the interpretation of G-ACGs given above does have some nice properties,
it fails to predict the intuitive understanding of more complex ACG
diagrams. This is most visible in the diamond-shaped grammar on
Figure~\ref{fig:diamond}. If we take a term from
$\mathcal{E}_{\mathcal{D}}(Bottom)$, we know it has antecedents both in
$\mathcal{E}_{\mathcal{D}}(Left)$ and
$\mathcal{E}_{\mathcal{D}}(Right)$. However, these two do not have to share an
antecedent in $\mathcal{E}_{\mathcal{D}}(Top)$. This contradicts the
generative story one might imagine in which a single term from $Top$ generates
terms in $Left$ and $Right$ which finally generate a term in $Bottom$.

@@

@@

\begin{align*}
A_{tatou} &: N_{NUM{=}SG} \\
A_{tatous} &: N_{NUM{=}PL} \\
A_{le} &: N_{NUM{=}SG} \limp NP_{NUM{=}SG} \\
A_{les} &: N_{NUM{=}PL} \limp NP_{NUM{=}PL} \\
A_{aime_1} &: NP_{NUM{=}SG} \limp NP_{NUM{=}SG} \limp S \\
A_{aime_2} &: NP_{NUM{=}SG} \limp NP_{NUM{=}PL} \limp S \\
A_{qui_1} &: (NP_{NUM{=}SG} \limp S) \limp N_{NUM{=}SG} \limp N_{NUM{=}SG} \\
A_{qui_2} &: (NP_{NUM{=}PL} \limp S) \limp N_{NUM{=}PL} \limp N_{NUM{=}PL}
\end{align*}

@@

However, it is important to keep in mind that the composability demonstrated
above is limited only to the composition of constraints. If we would like to
extend our language with, e.g., a new lexical category, then every signature
and every lexicon would have to be extended to cover this new category. It is
also important to point out that the constraint signatures that we have been
composing are not light-weight objects. They are usually defined by taking an
existing signature that describes the language at a relevant level and by
strengthening (usually all) the types of that signature to enforce the
constraint\footnote{This makes the expressivity of model-theoretic syntactic
  formalisms formalisms such as Interaction Grammars, in which adding the
  lexical items for \emph{ne} and \emph{aucun} along with enforcing the $Neg$
  constraint takes only two tree descriptions \cite{perrier2007french}, even
  more striking when compared to our approach.}. However, most of these type
alterations are mundane and we believe that this is fertile ground for
applying metagrammars.

@@

In the end, our approach us define the syntax in a clean way using the
idiomatic style of categorial grammars (simple atomic types like $N$, $NP$ and
$S$) and then define the constraints themselves the same way as they are
defined in ACG research (such as is the case with
\cite{pogodalla2012controlling}).

Interesting avenues of future work include: digging deeper into the
language-theoretical properties of G-ACGs (Are ACG object languages closed on
intersection? Are pangraphical languages expressible as extrinsic languages?),
searching for a metagrammatical description of constraint signatures to ease
work on G-ACG grammars and finally building large-scale grammars to verify the
utility of our approach.

>>>>

\mainmatter              % start of the contributions
%
\title{Integration of Multiple Constraints in ACG}
%
\titlerunning{Constraints in ACG}  % abbreviated title (for running head)
%                                    also used for the TOC unless
%                                    \toctitle is used
%
\author{Jiří Maršík\inst{1,2,3} \and Maxime Amblard\inst{1,2,3}}
%
\authorrunning{Maršík et al.} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\tocauthor{Jiří Maršík and Maxime Amblard}
%
\institute{Université de Lorraine, Laboratoire lorrain de recherche en informatique et ses applications, UMR 7503, Vandoeuvre-lès-Nancy, 54500, France\\
\and
INRIA, Villers-lès-Nancy, 54600, France\\
\and
CNRS, Loria, Vandoeuvre-lès-Nancy, UMR 7503, 54500, France\\
\email{\{jiri.marsik, maxime.amblard\}@loria.fr}}

@@

@@

\vspace{-4ex}

@@

\vspace{-1ex}

@@

If we were to use this approach to write a grammar that enforces multiple
constraints at the same time, we would end up with complicated types, like the
one below, which provide complete specifications of the various possible
situations (in this grammar ($C$), the preposition \emph{de} has 12 different
types).

\vspace{-4ex}

@@

We would like to have a system which would be characterized by a diagram like
the one on Figure~\ref{fig:gacg} where the constraint signatures delimit the
legal syntactic structures independently of each other and without interfering
with the syntax-semantics interface. However, ACG diagrams are limited to
arborescences and we are obliged to generalize them in order to get
the expected interpretation.

@@

While the interpretation of G-ACGs given above does have some nice properties,
it fails to predict the intuitive understanding of more complex ACG
diagrams. This is most visible in the diamond-shaped grammar on
Figure~\ref{fig:diamond}. If we take a term from
$\mathcal{E}_{\mathcal{D}}(Bottom)$, we know it has antecedents both in
$\mathcal{E}_{\mathcal{D}}(Left)$ and
$\mathcal{E}_{\mathcal{D}}(Right)$. However, these two do not have to share an
antecedent in $\mathcal{E}_{\mathcal{D}}(Top)$. This contradicts the
generative story one might imagine in which a single term from $Top$ generates
terms in $Left$ and $Right$ which generate a term in $Bottom$.

@@

\vspace{-3ex}

@@

\vspace{-3ex}

\begin{align*}
A_{tatou} &: N_{NUM{=}SG} \\
A_{tatous} &: N_{NUM{=}PL} \\
A_{le} &: N_{NUM{=}SG} \limp NP_{NUM{=}SG} \\
A_{les} &: N_{NUM{=}PL} \limp NP_{NUM{=}PL} \\
A_{aime_1} &: NP_{NUM{=}SG} \limp NP_{NUM{=}SG} \limp S \\
A_{aime_2} &: NP_{NUM{=}SG} \limp NP_{NUM{=}PL} \limp S
\end{align*}
\begin{align*}
A_{qui_1} &: (NP_{NUM{=}SG} \limp S) \limp N_{NUM{=}SG} \limp N_{NUM{=}SG} \\
A_{qui_2} &: (NP_{NUM{=}PL} \limp S) \limp N_{NUM{=}PL} \limp N_{NUM{=}PL}
\end{align*}

@@

However, it is important to keep in mind that the composability demonstrated
above is limited only to the composition of constraints. If we would like to
extend our language with, e.g., a new lexical category, then every signature
and every lexicon would have to be extended to cover this new category. It is
also important to point out that the constraint signatures that we have been
composing are not light-weight objects. They are usually defined by taking an
existing signature that describes the language at a relevant level and by
strengthening (usually all) the types of that signature to enforce the
constraint\footnote{This makes the expressivity of model-theoretic syntactic
  formalisms such as Interaction Grammars, in which adding the lexical items
  for \emph{ne} and \emph{aucun} along with enforcing the $Neg$ constraint
  takes only two tree descriptions \cite{perrier2007french}, even more
  striking when compared to our approach.}. However, most of these type
alterations are mundane and we believe that this is fertile ground for
applying metagrammars.

@@

In the end, our approach lets us define the syntax in a clean way using the
idiomatic style of categorial grammars (simple atomic types like $N$, $NP$ and
$S$) and then define the constraints themselves the same way as they are
defined in ACG research (such as is the case with
\cite{pogodalla2012controlling}).

Interesting avenues of future work include: digging deeper into the
language-theoretical properties of G-ACGs (Are ACG object languages closed on
intersection? Are extrinsic languages as expressive as pangraphical
languages?), searching for a metagrammatical description of constraint
signatures to ease work on G-ACG grammars and finally building large-scale
grammars to verify the usability of our approach.
